Do explicitly polarizable force fields give better description of biomembranes?

### 2023-10-14 manuscriptPOL.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title[An \textsf{achemso} demo]
%  {A demonstration of the \textsf{achemso} \LaTeX\
%   class\footnote{A footnote for the title}}
%\title{NMRLipids VI: Polarizable Force Fields}
\title{Do explicitly polarizable force fields give better description of a biomembrane?}
%\title{Comparison of polarizable lipid models to high-resolution experimental data reveals room for improvement}
%\title{Benchmarking polarizable lipid force field}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

	For the initial project description, please refer to \\ https://github.com/batukav/NMRlipidsVIpolarizableFFs/blob/master/Manuscript/manuscript.pdf

@@

In conventional molecular dynamics (MD) simulations, electrostatic interactions are described by assigning static point charges to the atoms and molecules at the beginning of the simulation based on the force field definitions. Dynamic effects arising from molecular polarizability are traditionally not explicitly included and are only considered in an averaged fashion in the force field parametrization process when fitting to macroscopic observables. Significant efforts have been dedicated to introduce explicit polarizability into MD simulations, in the hopes of reaching a more accurate representation of the system~\cite{Thole1981,ando2001stable,Grossfield2003,
lamoreux2003,Antila2013 ,Lemkul2016, baker2015polarizable,jing2019polarizable }. For bilayer membrane simulation, including polarizability in the lipids is expected to provide more accurate descriptions, especially in situations pertaining to membrane binding processes, translocation of charged biomolecules across the membrane, and the behavior of molecules residing within membranes, such as membrane proteins~\cite{baker2015polarizable,Lemkul2016, li2017drude,chu2018anionicpolarizable,Lynch21,Chen2021,Melcr:2018a, melcr2019improved,nencini22}. 
%Indeed, even implicit inclusion of polarizability appears to provide a better description of cation binding to membranes~\cite{Melcr:2018a, melcr2019improved}. 
The main lipid force fields with explicit electronic polarization are CHARMM-Drude~\cite{li2017drude, yu2023drude}, AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable}, and CHARMM-Fluctuating Charge (FQ)~\cite{lucas2012charge}. The underlying treatment of polarizability differ among these models in the following way:  1) the classical Drude oscillator (CHARMM-Drude) models polarization by separating a core and a shell charge with a spring which stretches according to the envinronment giving the site a dipole moment~\cite{Lemkul2016},
2) the induced point dipole/multipole (AMOEBA) uses polarizable point dipoles placed on chosen sites of the molecule~\cite{ponder2010current},
and 3) the electronegativity equilization (FQ) employs atomic charges that are no longer constant but can change according to the electronegativities of the molecule atoms and the electric fields from the molecular enviroment~\cite{patel2004charmm}. All of these approaches result in an increasing computational cost, e.g, by introducing new types of interactions, more interactions sites, or by requiring a shorter time step in the simulations. As an alternative approach, electronic continuum correction (ECC) has been proposed as a computational efficient method to implicitly include polarizability by scaling the atom partial charges~\cite{Melcr:2018a,dijon20,Antila2021}.

@@

Our previous efforts in benchmarking state-of-the-art non-polarizable force fields have demonstrated that the quality of predictions for important membrane properties greatly vary between different force fields, particularly for lipid headgroup conformational ensembles and ion binding affinities~\cite{Botan2015,Catte2016,Antila2019,bacle21,Antila2021,Antila2022,Databank}. This emphasizes the critical importance of rigorous comparative quality evaluations of simulations performed using different force fields, which helps to estimate the reliability of simulation results and select the best models for specific applications. This is particularly important when employing polarizable force fields, as they offer the potential to capture a broader range of physical phenomena pertinent to enhancing our understanding of in particular polar membrane regions, at an increased computational cost. Unfortunately, systematic benchmark studies assessing the quality of polarizable force fields are,  
%is in great need. The few published studies reviewing the state of polarizable force fields for biomolecule simulations did not go beyond citing results from the existing studies
to our knowledge, entirely missing from the field~\cite{inakollu2020polarisable,jing2019polarizable,baker2015polarizable}. Previous simulations using polarizable lipid force fields center around protein systems, with experimental validation (if performed at all) fovcusing on the properties of the proteins~\cite{jing2019polarizable, Lynch21}. Assessing the realism of the lipid models against experimental evidence from biophysical measurements is crucial since these membrane properties are foundational to more complicated applications, such as studies of transmembrane proteins. For example, it appears to be important that a wide variety of conformations is available for lipid headgroups in the model for realistic protein-lipid binding~\cite{bacle21}.

Here we set out to assess the quality of available polarizable force fields, on par with previous evaluations of non-polarizable force fields, using the resources given by the NMRLipids open collaboration framework (https://databank.nmrlipids.fi/). Specifically, we evaluated the quality of POPC, DOPC and POPE lipid bilayer simulations with CHARMM-Drude~\cite{li2017drude,yu2023drude} and AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters against experimental NMR and small angle X-ray scattering (SAXS) data. These two force fields are increasingly utilized in biomolecular simulations and have lipid parameters available for the selected systems with corresponding experimental data available from the NMRlipids databank~\cite{Databank}. Following the quality metrics defined in the NMRlipids project, structural properties and cation binding were evaluated against NMR order parameters and SAXS form factors~\cite{Botan2015,ollila16,Catte2016,Databank}, while lipid conformational dynamics was evaluated in comparison to data from NMR spin relaxation rate experiments~\cite{ferreira15,Antila2021}. 
%Small angle scattering (SAXS) data is used to estimate the description of electron density profile of the membrane. 
Furthermore, we compare the results to those obtained from the best performing non-polarizable simulations from the NMRlipids Databank\cite{Databank}.

@@

To evaluate the structural properties of lipid bilayers in simulations with polarizable force fields, we simulated POPC and POPE lipid bilayers with CHARMM-Drude2017~\cite{li2017drude} and CHARMM-Drude2023~\cite{yu2023drude} parameters, and POPE and DOPC bilayers with AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters. These systems were selected based on simultaneous availability of force field parameters, and experimental data~\cite{Databank}. After the data production, simulation trajectories were added into the NMRlipids Databank (https://github.com/NMRLipids/Databank/) and the NMRlipids quality metrics was used to evaluate each simulation against experiments~\cite{Databank}. This metric measures the quality of conformational ensemble of individual lipids in two aspects: first, it evaluates agreement with C-H bond order parameters (from NMR), and second, it examines consistency of membrane dimensions compared to small angle X-ray scattering (SAXS) data~\cite{Databank,ollila16}. 
%(measuring the electron density variation across the membrane). 
The former is divided into three parts that separately describe the average quality of headgroup, glycerol backbone and acyl chain qualities as described in the NMRlipids databank~\cite{Databank}. While order parameters primarily reflect lipid conformations, acyl chain order parameters are also a good proxy for membrane packing since a smaller area per lipid tends to increase the magnitude of the order parameters~\cite{Databank}. 
%one for each of the carbonyl tails, and the quality of each is evaluated separately.

@@

\begin{table}[]
    \centering
    \begin{tabular}{c c c c c c c}
        Lipid & Force field & $P^{\mathrm{headgroup}}$ & $P^{sn-1}$ & $P^{sn-2}$ & $FF_{q}$ & APL \\
        \hline
        POPC & OPLS3e       & 0.76 & 0.87 & 0.85 & 0.15 & 66.5\\
        POPC & CHARMM36     & 0.70 & 0.54 & 0.69 & 1.16 & 65.0\\
        POPC & CHARMM-Drude & 0.52 & 0.29 & 0.53 & 1.06 & 62.5\\
        POPC & CHARMM-Drude2023 & 0.63 & 0.60 & 0.57 & 0.96 & 64.5\\
        \hline
        POPE & GROMOS-CKP & 0.29 & 0.83 & 0.48 & 0.40 & 59.6\\
        POPE & CHARMM36   & 0.54 & 0.52 & 0.27 & 1.30 & 57.2 \\
        POPE & CHARMM-Drude & 0.06 & 0.53 & 0.27 & 0.80 & 56.6  \\
        POPE & CHARMM-Drude2023 & 0.28 & 0.59 & 0.54 & 0.00 & 61.4  \\
        POPE & AMOEBA & 0.21 & 0.10 & 0.23 & 3.80 & 66.9\\
        \hline
        DOPC & AMOEBA & 0.60 & 0.60 & 0.54 & - & 70.2\\
    \end{tabular}
    \caption{NMRlipids databank quality metrics~\cite{Databank} and area per lipids (APL) compared between the best simulations found from the NMRlipids databank (OPLS3e for POPC and GROMOS-CKP for POPE), simulations with CHARMM36 force field, and simulations with polarizable force fields. Order  parameter quality measures, $P^{\mathrm{headgroup}}$, $P^{sn-1}$, and $P^{sn-2}$, present the average probability of order parameters within a given segment to agree with experiments (larger probabilities mean higher quality). Form factor quality measure, $FF_{q}$, presents the difference in essential features between simulated and experimental form factors (smaller values indicate higher quality). Experimental estimations for areas per lipid are POPC: 64.3$\pm1$\AA$^{2}$\cite{kucerka2011}, DOPC: 67.5$\pm1$\AA$^{2}$\cite{kucerka2008}, and POPE: 56.7$\pm$3\AA$^{2}$\cite{Rickeard2020}.}
    \label{tab:my_label}
\end{table}

@@

Direct comparisons between simulated and experimental data are visualized in Fig~\ref{fig:order_parameters} and the resulting quality metrics are shown in Table~\ref{tab:my_label}. Similarly to the non-polarizable CHARMM36 simulations with Gromacs, CHARMM-Drude simulation predicts slightly too packed membrane with excessively negative order parameters with respect to experiments and simulations with the highest quality in the NMRlipids databank (OPLS3e)~\cite{Databank}. However,
%consistently outperform the polarizable force fields with respect to the NMR measurables for all parts of the molecule (higher $P$-values). For older CHARMM-Drude force field, 
the quality of headgroup conformations in the CHARMM-Drude simulations is worse than in its non-polarizable counterpart. This is likely because headgroup and glycerol backbone parameters were optimized to reproduce absolute average values of the experimentally determined order parameters, instead of taking into account the order parameter forking (meaning measurably different order parameters for different C--H bonds at a single carbon atom) and order parameter sign~\cite{Antila2022}. A better description of the headgroup and glycerol backbone is provided by CHARMM36-Drude2023, yet its quality is still below that offered by the non-polarizable CHARMM36 parameters (see also discussion about conformational dynamics below). Also the quality of membrane packing and acyl chain order are improved in CHARMM36-Drude2023 compared to the earlier version but again, it did not perform at a quality comparable to that of the best available simulations.
%also provides better description of the carbon tails. 
%In fact, for POPE sn-2 tail the CHARMM-Drude2023 gives the best description of the models investigated here.

@@

\subsection{Evaluation of conformational dynamics of lipids}
C-H bond order parameters are sensitive to the conformational ensemble but the correspondence is not unique. Instead, they essentially describe the average of the distributions and do not contain information of the dynamics of the confomational sampling. Therefore, a simulation that reproduces the order parameters has an ensemble that is only potentially correct, and even the correct ensemble may not have the experimentally observed dynamics. To further elucidate this aspect in the case of polarizable force fields, we compared NMR $^{13}$C spin relaxation $R_{1}$ rates and C-H bond effective correlation times $\tau_{\mathrm{eff}}$ with experiments~\cite{ferreira15} and best non-polarizable simulations from our previous study~\cite{Antila2021} for simulations with PC headgroups and the glycerol backbone in Fig.~\ref{fig:correlation_times}. This focus was chosen based on the availability of both experimental data and polarizable simulations. $R_{1}$ rates measured with typical magnetic field strengths are sensitive to rotational dynamics of C-H bonds with the timescales around $\sim$0.1-1~ns, while effective correlation times respond to a larger range of dynamical processes up to $\sim$1000~ns~\cite{ferreira15}. The effective correlation time can be interpreted as an average measure for how fast molecular conformations sample the phase space that leads to the average order parameters.

@@

Given the abundance of cations in biological systems, accurately capturing their interactions with membranes has the uttermost importance in MD simulations. A wealth of  experimental evidence shows that monovalent ions, such as sodium (except for lithium), exhibit very weak binding affinity of PC lipid bilayers, while multivalent ions like calcium bind more strongly~\cite{Catte2016}. However, simulations with non-polarizable force fields without any additional corrections systematically overestimate cation binding to lipid bilayers~\cite{Catte2016}. Implicit inclusion of electronic continuum correction (ECC) to both ion and lipid parameters can substantially improve the situation~\cite{Melcr:2018a,melcr2019improved,bacle21}, suggesting that electronic polarizability plays an important role in ion binding to membranes, which might further lead one to expect that that simulations with polarizable force fields will perform better in this aspect and more accurately describe ion binding to membranes.
%Finally, we address the premise that adding polarizability to force fields improves the depiction of ion binding to biomembranes in simulations. 
To test this notion, we evaluated sodium and calcium cation binding to membranes against the experimental NMR data using the "lipid electrometer," which involves quantifing the amount of ion binding to the membrane by monitoring the change in lipid headgroup order parameters in response to increasing salt concentration~\cite{Catte2016}. Changes in these order parameters induced by increasing NaCl and CaCl$_2$ are shown in Fig.~\ref{fig:popc_order_parameter_change} for simulations and experiments, whereas Fig.~\ref{fig:ion_density_profiles} shows the density profiles of ions with respect to the bilayer normal. Results from AMBER-based ECC-lipid model are shown for the reference that gives a good agreement with experiments for cation binding.

\begin{figure}[!hbt]
	\centering
	\includegraphics{Figures/order_parameter_change.png}
	\caption{The change in the lipid head group order parameters $\beta$ (top row) $\alpha$ (bottom row) upon increasing ion concentration with respect to the simulations without salt. }
	\label{fig:popc_order_parameter_change}
\end{figure}

\begin{figure}[!hbt]
    \centering
    \includegraphics{Figures/ion_density_profiles_with_chloride.eps}
    \caption{Density profiles along the membrane normal for the CHARMM36 (first row)~\cite{Catte2016}, Drude 2017 and 2023 POPC (second and third rows), AMOEBA DOPC (fourth row), and electronic continuum correction (ECC, last row)~\cite{Melcr:2018a}. Solid and dashed lines are for the systems with the NaCl and CaCl$_{2}$, respectively. Please note that only 350~mM and 450~mM CaCl$_{2}$ concentrations are shown for the Drude and AMOEBA force fields, respectively, while 1000~mM NaCl concentration is shown for all force fields. CHARMM36 NaCl simulations are at 950~mM.}
    \label{fig:ion_density_profiles}
            \todo{SAMULI: We should also show the ion density profiles along membrane normal and compare the ones with 1000 mM NaCl and 350 mM CaCl$_2$
          (concentration in bulk water) to the best profiles in the literature (Fig. 5 in http://dx.doi.org/10.1021/acs.jpcb.7b12510).
          This will show the actual difference in ion binding to the best performing models available.}
          \todo{Batuhan: Data generated from http://dx.doi.org/10.1021/acs.jpcb.7b12510}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title[An \textsf{achemso} demo]
%  {A demonstration of the \textsf{achemso} \LaTeX\
%   class\footnote{A footnote for the title}}
%\title{NMRLipids VI: Polarizable Force Fields}
\title{Do explicitly polarizable force fields give better description of biomembranes?}
%\title{Comparison of polarizable lipid models to high-resolution experimental data reveals room for improvement}
%\title{Benchmarking polarizable lipid force field}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
With the increase of available computational capabilities, polarizable molecular dynamics force fields have gained popularity in modelling biomolecular systems. In the case of biomembranes in particular, they are expected to provide better description, eg., by capturing the varying dielectric environment across the lipid bilayer. Here, we use the framework established within the NMRlipids open science project and the related NMRlipids databank to test the commonly used polarizable lipid models, CHARMM-Drude and Amoeba, against high fidelity experimental data and best non-polarizable models. We find that, for each property tested, the best non-polarizable models surpass the polarizable ones. The flaws detected range from inaccuracies in describing the conformational space of lipid tails (AMOEBA) to the drastically too slow conformational dynamics of CHARMM-Drude models. That said, there is no model, polarizable or non-polarizable, that is consistently the best across all the properties tested.

%	For the initial project description, please refer to \\ https://github.com/batukav/NMRlipidsVIpolarizableFFs/blob/master/Manuscript/manuscript.pdf

@@

In conventional molecular dynamics (MD) simulations, electrostatic interactions are described by assigning static point charges to the atoms and molecules at the beginning of the simulation based on the force field definitions. Dynamic effects arising from molecular polarizability are traditionally not explicitly included and are only considered in an averaged fashion in the force field parametrization process when fitting to macroscopic observables. Significant efforts have been dedicated to introduce explicit polarizability into MD simulations, in the hopes of reaching a more accurate representation of the system~\cite{Thole1981,ando2001stable,Grossfield2003,
lamoreux2003,Antila2013 ,Lemkul2016, baker2015polarizable,jing2019polarizable }.

For bilayer membrane simulation, including polarizability in the lipids is expected to provide more accurate descriptions, especially in situations pertaining to membrane binding processes, translocation of charged biomolecules across the membrane, and the behavior of molecules residing within membranes, such as membrane proteins~\cite{baker2015polarizable,Lemkul2016, li2017drude,chu2018anionicpolarizable,Lynch21,Chen2021,Melcr:2018a, melcr2019improved,nencini22}. 
%Indeed, even implicit inclusion of polarizability appears to provide a better description of cation binding to membranes~\cite{Melcr:2018a, melcr2019improved}. 
The available lipid force fields with explicit electronic polarization include CHARMM-Drude~\cite{li2017drude, yu2023drude}, AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable}, and CHARMM-Fluctuating Charge (FQ)~\cite{lucas2012charge}. The underlying treatment of polarizability differ among these models in the following way:  1) the classical Drude oscillator (CHARMM-Drude) models polarization by separating a core and a shell charge with a spring which stretches according to the envinronment giving the site a dipole moment~\cite{Lemkul2016},
2) the induced point dipole/multipole (AMOEBA) uses polarizable point dipoles placed on chosen sites of the molecule~\cite{ponder2010current},
and 3) the electronegativity equilization (FQ) employs atomic charges that are no longer constant but can change according to the electronegativities of the molecule atoms and the electric fields from the molecular enviroment~\cite{patel2004charmm}. All of these approaches result in an increasing computational cost, e.g, by introducing new types of interactions, more interactions sites, or by requiring a shorter time step in the simulations. As an alternative approach, electronic continuum correction (ECC) has been proposed as a computational efficient method to implicitly include polarizability by scaling the atom partial charges~\cite{Melcr:2018a,dijon20,Antila2021}.

@@

Our previous efforts in benchmarking state-of-the-art non-polarizable force fields have demonstrated that the quality of predictions for important membrane properties greatly vary between different force fields, particularly for lipid headgroup conformational ensembles and ion binding affinities~\cite{Botan2015,Catte2016,Antila2019,bacle21,Antila2021,Antila2022,Databank}. Such benchmark studies are urgent also for polarizable lipid force fields, 
%are,  
%is in great need. The few published studies reviewing the state of polarizable force fields for biomolecule simulations did not go beyond citing results from the existing studies
%to our knowledge, entirely missing from the field
%~\cite{inakollu2020polarisable,jing2019polarizable,baker2015polarizable}  
%This emphasizes the critical importance of rigorous comparative quality evaluations of simulations performed using different force fields, which helps to estimate the reliability of simulation results and select the best models for specific applications. 
especially because their pledge is
%important when employing polarizable force fields, as they offer the potential 
to capture a broader range of physical phenomena pertinent to enhancing our understanding of in particular polar membrane regions.
%, at an increased computational cost. 
%Previous simulations using polarizable lipid force fields center around protein systems, with experimental validation (if performed at all) fovcusing on the properties of the proteins~\cite{jing2019polarizable, Lynch21}. 
Assessing quality of lipid models against experiments is crucial because membrane properties are fundamental in many applications where simulations are used to shed light on behaviour of complex biomolecular systems, such as studies of transmembrane proteins~\cite{jing2019polarizable, Lynch21}. For example, ion binding affinity regulates membrane surface charge and wide variety of conformations available for lipid headgroups appears to be important for modeling realistic protein-lipid binding~\cite{bacle21}.

Here we set out to assess the quality of actively developed polarizable lipid force fields, CHARMM-Drude~\cite{li2017drude,yu2023drude} and  AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable}, on par with previous evaluations of non-polarizable force fields, using the resources given by the NMRLipids open collaboration framework (\url{http://nmrlipids.blogspot.fi/}). These two force fields were selected for comparison because they are increasingly utilized in biomolecular simulations and have parameters available for the selected lipids with corresponding experimental data available from the NMRlipids databank~\cite{Databank}. We evaluated the structural quality of POPC, DOPC and POPE lipid bilayer simulations against experimental NMR and small angle X-ray scattering (SAXS) data using the quality metrics defined in the NMRlipids databank~\cite{Databank}. Cation binding to membranes was evaluated against NMR order parameters~\cite{Catte2016} and lipid conformational dynamics was evaluated in comparison to data from NMR spin relaxation rate experiments~\cite{ferreira15,Antila2021}. 
%Small angle scattering (SAXS) data is used to estimate the description of electron density profile of the membrane. 
Furthermore, we compare the results to those obtained from the best performing non-polarizable simulations from the NMRlipids Databank\cite{Databank}.

@@

To evaluate the structural properties of lipid bilayers in simulations with polarizable force fields, we simulated POPC and POPE lipid bilayers with CHARMM-Drude2017~\cite{li2017drude} and CHARMM-Drude2023~\cite{yu2023drude} parameters, and POPE and DOPC bilayers with AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters. These systems were selected based on simultaneous availability of force field parameters, and experimental data~\cite{Databank}. After the data production, simulation trajectories were added into the NMRlipids Databank and its quality metrics was used to evaluate each simulation against experiments~\cite{Databank}. This metric measures the quality of lipid bilayer simulations in two aspects: first, it evaluates the quality of conformational ensemble of individual lipids against C-H bond order parameters from NMR, and second, it examines consistency of membrane dimensions compared to small angle X-ray scattering (SAXS) data~\cite{Databank,ollila16}. 
%(measuring the electron density variation across the membrane). 
The former is divided into three parts that separately describe the average quality of headgroup, glycerol backbone and acyl chain qualities as described in the NMRlipids databank~\cite{Databank}. While order parameters primarily reflect lipid conformations, acyl chain order parameters are also a good proxy for membrane packing since a smaller area per lipid tends to increase the magnitude of the order parameters~\cite{Databank}. 
%one for each of the carbonyl tails, and the quality of each is evaluated separately.

@@

\begin{table}[]
    \centering
    \begin{tabular}{c c c c c c c}
        Lipid & Force field & $P^{\mathrm{headgroup}}$ & $P^{sn-1}$ & $P^{sn-2}$ & $FF_{q}$ & APL \\
        \hline
        POPC & OPLS3e       & 0.76 & 0.87 & 0.85 & 0.15 & 66.5\\
        POPC & CHARMM36     & 0.70 & 0.54 & 0.69 & 1.16 & 65.0\\
        POPC & CHARMM-Drude & 0.52 & 0.29 & 0.53 & 1.06 & 62.5\\
        POPC & CHARMM-Drude2023 & 0.63 & 0.60 & 0.57 & 0.96 & 64.5\\
        \hline
        POPE & GROMOS-CKP & 0.29 & 0.83 & 0.48 & 0.40 & 59.6\\
        POPE & CHARMM36   & 0.54 & 0.52 & 0.27 & 1.30 & 57.2 \\
        POPE & CHARMM-Drude & 0.06 & 0.53 & 0.27 & 0.80 & 56.6  \\
        POPE & CHARMM-Drude2023 & 0.28 & 0.59 & 0.54 & 0.00 & 61.4  \\
        POPE & AMOEBA & 0.21 & 0.10 & 0.23 & 3.80 & 66.9\\
        \hline
        DOPC & AMOEBA & 0.60 & 0.60 & 0.54 & - & 70.2\\
    \end{tabular}
    \caption{NMRlipids databank quality metrics~\cite{Databank} and area per lipids (APL) compared between the best simulations found from the NMRlipids databank (OPLS3e~\cite{roos19} for POPC and GROMOS-CKP~\cite{Chandrasekhar03,kukol09,piggot12} for POPE), simulations with CHARMM36 force field, and simulations with polarizable force fields. Order  parameter quality measures, $P^{\mathrm{headgroup}}$, $P^{sn-1}$, and $P^{sn-2}$, present the average probability of order parameters within a given segment to agree with experiments (larger probabilities mean higher quality). Form factor quality measure, $FF_{q}$, presents the difference in essential features between simulated and experimental form factors (smaller values indicate higher quality). Experimental estimations for areas per lipid are POPC: 64.3$\pm1$\AA$^{2}$\cite{kucerka2011}, DOPC: 67.5$\pm1$\AA$^{2}$\cite{kucerka2008}, and POPE: 56.7$\pm$3\AA$^{2}$\cite{Rickeard2020}.}
    \label{tab:my_label}
\end{table}

@@

Direct comparisons between simulated and experimental data are visualized in Fig~\ref{fig:order_parameters} and the resulting quality metrics are shown in Table~\ref{tab:my_label}. Similarly to the non-polarizable CHARMM36 simulations, CHARMM-Drude simulation predicts slightly too packed membrane with excessively negative order parameters with respect to experiments and simulations with the highest quality in the NMRlipids databank (OPLS3e)~\cite{Databank}. However,
%consistently outperform the polarizable force fields with respect to the NMR measurables for all parts of the molecule (higher $P$-values). For older CHARMM-Drude force field, 
the quality of headgroup conformations in the CHARMM-Drude simulations is worse than in its non-polarizable counterpart. This is likely because headgroup and glycerol backbone parameters were optimized to reproduce absolute average values of the experimentally determined order parameters, instead of taking into account the order parameter forking (meaning measurably different order parameters for different C--H bonds at a single carbon atom) and order parameter sign~\cite{Antila2022}. A better description of the headgroup and glycerol backbone is provided by CHARMM36-Drude2023, yet its quality is still below that offered by the non-polarizable CHARMM36 parameters (see also discussion about conformational dynamics below). Also the quality of membrane packing and acyl chain order are improved in CHARMM36-Drude2023 compared to the earlier version but again, it did not perform at a quality comparable to that of the best available simulations.
%also provides better description of the carbon tails. 
%In fact, for POPE sn-2 tail the CHARMM-Drude2023 gives the best description of the models investigated here.

@@

\subsection{Evaluation of conformational dynamics of lipids}
C-H bond order parameters are sensitive to the conformational ensemble but the correspondence is not unique. Instead, they essentially describe the average of the distributions and do not contain information of the dynamics of the conformational sampling. Therefore, a simulation that reproduces the order parameters has an ensemble that is only potentially correct, and even the correct ensemble may not have the experimentally observed dynamics. To further elucidate this aspect in the case of polarizable force fields, we compared NMR $^{13}$C spin relaxation $R_{1}$ rates and C-H bond effective correlation times $\tau_{\mathrm{eff}}$ with experiments~\cite{ferreira15} and best non-polarizable simulations from our previous study~\cite{Antila2021} for simulations with PC headgroups and the glycerol backbone in Fig.~\ref{fig:correlation_times}. This focus was chosen based on the availability of both experimental data and polarizable simulations. $R_{1}$ rates measured with typical magnetic field strengths are sensitive to rotational dynamics of C-H bonds with the timescales around $\sim$0.1-1~ns, while effective correlation times respond to a larger range of dynamical processes up to $\sim$1000~ns~\cite{ferreira15}. The effective correlation time can be interpreted as an average measure for how fast molecular conformations sample the phase space that leads to the average order parameters.

@@

Given the abundance of cations in biological systems, accurately capturing their interactions with membranes has the uttermost importance in MD simulations. A wealth of  experimental evidence shows that monovalent ions (except for lithium) exhibit very weak binding affinity of PC lipid bilayers, while multivalent ions like calcium bind more strongly~\cite{Catte2016}. However, simulations with non-polarizable force fields without any additional corrections systematically overestimate cation binding to lipid bilayers~\cite{Catte2016}. Implicit inclusion of electronic continuum correction (ECC) to both ion and lipid parameters can substantially improve the situation~\cite{Melcr:2018a,melcr2019improved,bacle21}, suggesting that electronic polarizability plays an important role in ion binding to membranes, which might further lead one to expect that that simulations with polarizable force fields will perform better in this aspect and more accurately describe ion binding to membranes.
%Finally, we address the premise that adding polarizability to force fields improves the depiction of ion binding to biomembranes in simulations. 
To test this notion, we evaluated ion binding to membranes against the experimental NMR data using the "lipid electrometer," which involves quantifing the amount of ion binding to the membrane by monitoring the change in lipid headgroup order parameters in response to increasing salt concentration~\cite{Catte2016}. Changes in these order parameters induced by increasing NaCl and CaCl$_2$ are shown in Fig.~\ref{fig:popc_order_parameter_change} for simulations and experiments, whereas Fig.~\ref{fig:ion_density_profiles} shows the density profiles of ions with respect to the bilayer normal. Results from AMBER-based ECC-lipid model are shown for the reference that gives a good agreement with experiments for cation binding. We also show data from the non-polarizable CHARMM36 where NBFIX correction for the ion models was specifically developed to address overbinding~\cite{Venable2013,Han2018}.

\begin{figure}[!hbt]
	\centering
	\includegraphics{Figures/order_parameter_change.png}
	\caption{The change in the lipid head group order parameters $\beta$ (top row) $\alpha$ (bottom row) upon increasing ion concentration with respect to the simulations without salt. CHARMM36 and ECC data is reproduced using the Zenodo repositories Ref.~\cite{ollila_2015_32496, ollila_2015_32497, ollila_2015_32498, nencini_ricky_2019_3434396} and Ref.~\cite{melcr_josef_2017_3335503}, respectively.}
	\label{fig:popc_order_parameter_change}
\end{figure}

\begin{figure}[!hbt]
    \centering
    \includegraphics{Figures/ion_density_profiles_with_chloride.eps}
    \caption{Density profiles along the membrane normal for the CHARMM36 (first row)~\cite{Catte2016}, Drude 2017 and 2023 POPC (second and third rows), AMOEBA DOPC (fourth row), and electronic continuum correction (ECC, last row)~\cite{Melcr:2018a}. Solid and dashed lines are for the systems with the NaCl and CaCl$_{2}$, respectively. Please note that only 350~mM and 450~mM CaCl$_{2}$ concentrations are shown for the Drude and AMOEBA force fields, respectively, while 1000~mM NaCl concentration is shown for all force fields. CHARMM36 NaCl simulations are at 950~mM. CHARMM36 data is reproduced using the Zenodo repositories Ref.~\cite{ollila_2015_32496, ollila_2015_32497, ollila_2015_32498, nencini_ricky_2019_3434396}}
    \label{fig:ion_density_profiles}
\end{figure}

The CHARMM-Drude2017 predicts similar calcium ion density profile to ECC-lipids, in good agreement with experiments. However, the sodium binding is equally strong in these simulations in contrast with the experimental evidence~\cite{Catte2016}. 
%, evidenced both by large change in the order parameters and the ion density profiles. Based on the change in the order parameters, the sodium binding is even stronger than the divalent calcium binding. In strong contrast, experimentally one sees no sodium binding and some binding of calcium ions. 
Excessive sodium binding in the CHARMM-Drude model has been observed before for systems containing peptides or amino acids~\cite{Ngo2019, Kav2022} and deep-eutectic solvents~\cite{shayestehpour2022ion}. Excessive calcium interactions, in line with what we observe here for the lipids, have also been reported~\cite{Tan2022}. Furthermore, the response of headgroup order parameters to the bound ions is not in qualitative agreement with experiments for CHARMM-Drude2017 simulations according to Fig.~\ref{fig:popc_order_parameter_change}. Particularly, increasing $\alpha$ carbon order parameters and forking upon ion binding are not observed in experiments. This is in contrast with the results from previous bechmarking of non-polarizable simulations~\cite{Catte2016}, where experimentally observed decrease of order parameters to more negative values upon ion binding were observed in all simulations, even though the binding affinity was often inaccurately predicted. This qualitative discrepancy in CHARMM-Drude2017 simulations most likely results from incorrect lipid headgroup conformational ensemble (see previous sections), which leads to inaccuracies in the structural response of the ensemble to ion binding.
